Boosting, Sparsity, and Conditional Gradient: A Tutorial

### 2014-02-19 arXiv/introduction.tex

The purpose of this paper is to serve as a tutorial on sparsification. While 
most of the results presented are known, they are often distributed across the 
theory, machine learning, and optimization literatures, and we hope to bring 
them all into one place, as well as to provide a unifying perspective.

>>>>

The purpose of this paper is to serve as a tutorial on sparsification as it arises 
in machine learning, computer science theory, and optimization. While most of the 
results presented are known, they are often distributed across the these 
literatures. Our objective is to bring them all into one place, 
as well as to provide a unifying perspective.
